Kids PM Summary

### 2020-07-17 exposure_models.Rmd
minor analysis updates

  na.exclude()
```

@@

# Compare imputed summary to original summary
summary(selected_vars)
summary(complete(imputed_data))

@@

# Can add "long" or "broad" arguments
complete(imputed_data, "long")

@@

```{r}
# Look at R^2 for final selected model
model_results <- lm(log_pm_mean_sampling_period ~
                      residents_smoke +
                      chimney_clean_3level +
                      stove_grade_3level,
                      data = imputed_exposure_data$data)

>>>>

  na.exclude()

  # Check % missing data
mean(is.na(selected_vars)) # 8% for WMT, 10% for NN, 16% for AK, 10% total
```

@@

# Compare imputed summary to original summary
summary(selected_vars)
summary(complete(imputed_exposure_data))

@@

# Can add "long" or "broad" arguments
complete(imputed_exposure_data, "long")

@@

```{r}
# Look at R^2 for final selected model
imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_2july2020.rds"))

model_data <- complete(imputed_exposure_data, "long")

model_results <- lm(log_pm_mean_sampling_period ~
                    income_3level + 
                    residents_smoke +
                    home_floors_2level +
                    home_sqft_2level +
                    stove_age_3level + 
                    chimney_clean_3level + 
                    sums_events_sampling_period_7.5 + 
                    mean_temp_sampling_period_5 + 
                    amb_pm_sampling_period_5 + 
                    stove_grade_3level + 
                    home_fireplace,
                    data = model_data)

### 2020-07-17 manuscript_tables_figures.Rmd
minor analysis updates

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

>>>>

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

### 2020-07-17 pm_summary.Rmd
minor analysis updates

#Pm by different levels of covariates
pm_check <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(chimney_clean_3level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_check

# closer look at stove grade and PM
pm_stove_grade <- exposure_analysis_data_short %>%
  select(area, home, pm_mean_sampling_period, stove_grade_3level, 
         treatment_assigned, winter_id, home_winter_id) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(stove_grade_2level = fct_collapse(stove_grade_3level,
                                           "A" = "A",
                                           "C or F" = c("C", "F"))) %>% 
  group_by(stove_grade_2level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_stove_grade

>>>>

#Pm by different levels of covariates
pm_check <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(pm_mean_sampling_period) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(chimney_clean_3level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_check

# closer look at stove grade and PM
pm_stove_grade <- health_exposure_data_sampling_day %>%
  select(area, home, pm_mean_sampling_period, stove_grade_3level, 
         treatment_assigned, winter_id, home_winter_id) %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(pm_mean_sampling_period) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(stove_grade_2level = fct_collapse(stove_grade_3level,
                                           "A" = "A",
                                           "C or F" = c("C", "F"))) %>% 
  group_by(stove_grade_2level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_stove_grade
